Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-06 gibbs.tex

@@

@@

\subsection{Study limitations}
TODO

\subsection{Implications and future perspectives}
TODO

>>>>

% Alternative titles
%\Title{What the Gibbs ensemble modeling says about water desalination using polyelectrolyte hydrogel}
%\Title{Water desalination using polyelectrolyte hydrogel from the Gibbs ensemble modeling point of view}

@@

\subsection{Study limitations}
Like other simulation based studies, our research has a limited validity,
primarily resulting from the simplifications applied in the used model.
For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.
However, these limitations are also the advantage of our model because the results of our study
can be applied to similar systems, including polybasic gels with all the charges reversed.

\subsection{Implications and future perspectives}
We are aware that the concept introduced in this simulation study need to be experimentally verified.
Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.

@@
